Analysis - expt 1

### 2024-01-10 code/analysis_1.Rmd
tweaked abstract
graph tweaks for talk

@@

acc_w_legend <- dat %>% left_join(exclusion) %>% filter(S_talked==1) %>% 
  mutate(type=case_when(trialNum<2 ~ "practice",
                        trialNum<6 ~ "block 1",
                        trialNum<10 ~ "block 2",
                        trialNum<14 ~ "block 3"),
         type=factor(type, levels=c("practice", "block 1", "block 2", "block 3"))) %>% 
  ggplot(aes(x = trialNum+1, y = as.numeric(correct), fill=type)) +
  stat_summary(fun.data="mean_cl_boot", geom="bar") +
    stat_summary(fun.data="mean_cl_boot", geom="linerange") +
  scale_fill_manual(values=time_palette)+
  theme_bw() +
  xlab("Trial") +
  ylab("Accuracy") +
  labs(fill="")+
  geom_hline(yintercept=.5, linetype="dashed")+
    coord_cartesian(ylim=c(0,1), expand=F)+
  theme(axis.text=element_text(size=10, color = "black"),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        #axis.title.x=element_blank(),
                axis.title=element_text(size=12),
        legend.text=element_text(size=12),
        legend.position = "bottom")

@@

speed_plot <- dat %>% left_join(exclusion) %>% filter(S_talked==1) %>% 
  mutate(type=case_when(trialNum<2 ~ "practice",
                        trialNum<6 ~ "block 1",
                        trialNum<10 ~ "block 2",
                        trialNum<14 ~ "block 3")) %>% 
  mutate(time=ifelse(is.na(time),180000,time)) %>% #treat the one that timed out as being max time
  ggplot(aes(x = trialNum+1, y = time/1000, color=type)) +
  geom_jitter(width=.2, height=0, alpha=.7)+
    stat_summary(fun.data="mean_cl_boot", geom="pointrange", color="black") +
  scale_color_manual(values=time_palette)+
  theme_bw() +
  ylab("Speed (seconds)")+
  xlab("Trial")+
  coord_cartesian(ylim=c(0,60), expand=F)+
  theme(axis.text=element_text(size=10, color = "black"),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
                axis.title=element_text(size=12),
        #axis.title.x=element_blank(),
        legend.position = "none")

word_plot <- transcript %>% filter(!is.na(description)) %>% group_by(game,speaker, trial) %>% 
  summarize(words=str_c(description, sep=" ", collapse=", ")) %>% 
  mutate(word_count=str_count(words, "\\S+")) %>% 
  mutate(type=case_when(trial<2 ~ "practice",
                        trial<6 ~ "block 1",
                        trial<10 ~ "block 2",
                        trial<14 ~ "block 3")) %>% 
  ggplot(aes(x = trial+1, y = word_count, color=type)) +
    geom_jitter(width=.2, height=0, alpha=.7)+
  #geom_line(aes(group=game))+
 # facet_wrap(.~correct) + 
    stat_summary(fun.data="mean_cl_boot", geom="pointrange", color="black") +
  scale_color_manual(values=time_palette)+
  #geom_bar(position = position_dodge(.9), color = "black", fill = "#19ADDE", width = .7) +
  #geom_smooth(method="lm")+
  #geom_text(aes(label = percent), hjust = 1.6, color = "white", size = 3) +
  theme_bw() +
  xlab("Trial") +
  ylab("Description length (words)")+
  coord_cartesian(ylim=c(0,20), expand=F)+
  #ylab("Percent trials with echoing \n by experimenter\n") +
  #scale_x_continuous(breaks=seq(1,12,1)) +
  #scale_y_continuous(breaks=seq(0,100,10), expand=c(0,0)) +
  theme(axis.text=element_text(size=10, color = "black"),
        axis.title=element_text(size=12),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        legend.position = "none")

plot_grid(acc_legend,acc_plot,speed_plot,word_plot, ncol=1, rel_heights = c(.2,.7,1,1), labels=c("","A", "B","C"), label_size = 18, label_x=0.12,label_y=.97 )

ggsave(here("write-ups/CAMP6/plot1.pdf"))
```

>>>>

data_for_mods %>% ungroup() %>% summarize(correct=sum(correct.num)/n())
```

@@

acc_dat <- dat %>% left_join(exclusion) %>% filter(S_talked==1) %>% 
  mutate(type=case_when(trialNum<2 ~ "practice",
                        trialNum<6 ~ "block 1",
                        trialNum<10 ~ "block 2",
                        trialNum<14 ~ "block 3"),
         type=factor(type, levels=c("practice", "block 1", "block 2", "block 3")))
  acc_w_legend <- ggplot(acc_dat, aes(x = trialNum+1, y = as.numeric(correct), color=type)) +
  stat_summary(data=acc_dat |> filter(type!="practice"), fun.data="mean_cl_boot", geom="line", color="black") +
    stat_summary(fun.data="mean_cl_boot", geom="pointrange") +
  scale_color_manual(values=time_palette)+
  theme_bw() +
  xlab("Trial") +
  ylab("Accuracy") +
  labs(fill="")+
  geom_hline(yintercept=.5, linetype="dashed")+
    coord_cartesian(ylim=c(0,1), expand=T)+
  theme(axis.text=element_text(size=10, color = "black"),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        #axis.title.x=element_blank(),
                axis.title=element_text(size=12),
        legend.text=element_text(size=12),
        legend.position = "bottom")

@@

speed_dat <- dat %>% left_join(exclusion) %>% filter(S_talked==1) %>% 
  mutate(type=case_when(trialNum<2 ~ "practice",
                        trialNum<6 ~ "block 1",
                        trialNum<10 ~ "block 2",
                        trialNum<14 ~ "block 3")) %>% 
  mutate(time=ifelse(is.na(time),180000,time)) #treat the one that timed out as being max time
 speed_plot <-  ggplot(speed_dat, aes(x = trialNum+1, y = time/1000, color=type)) +
  geom_jitter(width=.2, height=0, alpha=.7)+
  stat_summary(data=speed_dat |> filter(type!="practice"), fun.data="mean_cl_boot", geom="line", color="black") +
    stat_summary(fun.data="mean_cl_boot", geom="pointrange", color="black") +
  scale_color_manual(values=time_palette)+
  theme_bw() +
  ylab("Speed (seconds)")+
  xlab("Trial")+
  coord_cartesian(ylim=c(0,60), expand=F)+
  theme(axis.text=element_text(size=10, color = "black"),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
                axis.title=element_text(size=12),
        #axis.title.x=element_blank(),
        legend.position = "none")

word_dat <- transcript %>% filter(!is.na(description)) %>% group_by(game,speaker, trial) %>% 
  summarize(words=str_c(description, sep=" ", collapse=", ")) %>% 
  mutate(word_count=str_count(words, "\\S+")) %>% 
  mutate(type=case_when(trial<2 ~ "practice",
                        trial<6 ~ "block 1",
                        trial<10 ~ "block 2",
                        trial<14 ~ "block 3"))
word_plot <- 
  ggplot(word_dat, aes(x = trial+1, y = word_count)) +
    geom_jitter(aes(color=type), width=.2, height=0, alpha=.7)+
  #geom_line(aes(group=game))+
 # facet_wrap(.~correct) + 
      stat_summary(data=word_dat |> filter(type!="practice"), fun.data="mean_cl_boot", geom="line", color="black") +
    stat_summary(fun.data="mean_cl_boot", geom="pointrange") +
  scale_color_manual(values=time_palette)+
  #geom_bar(position = position_dodge(.9), color = "black", fill = "#19ADDE", width = .7) +
  #geom_smooth(method="lm")+
  #geom_text(aes(label = percent), hjust = 1.6, color = "white", size = 3) +
  theme_bw() +
  xlab("Trial") +
  ylab("Description length (words)")+
  coord_cartesian(ylim=c(0,20), expand=F)+
  #ylab("Percent trials with echoing \n by experimenter\n") +
  #scale_x_continuous(breaks=seq(1,12,1)) +
  #scale_y_continuous(breaks=seq(0,100,10), expand=c(0,0)) +
  theme(axis.text=element_text(size=10, color = "black"),
        axis.title=element_text(size=12),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        legend.position = "none")

plot_grid(acc_plot,speed_plot,word_plot, ncol=1, rel_heights = c(1,1,1)) #labels=c("","A", "B","C"), label_size = 18, label_x=0.12,label_y=.97 )

ggsave(here("write-ups/CAMP6/plot1.png"))
```

```{r}
plot_grid(acc_legend)

ggsave(here("write-ups/CAMP6/legend.pdf"), width=6, height=2)
